\documentclass{article}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage[margin=1.3in]{geometry}

\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
}

% For numbered references
\usepackage[numbers]{natbib}
\usepackage{bibentry}

\nobibliography*

% No indenting
\setlength\parindent{0pt}

\usepackage{titling}
\setlength{\droptitle}{-6em}   % This is your set screw

\title{MTH 4320/5320 References}

\date{}

\begin{document}

\maketitle

\vspace{-6em}

\section*{Books}

\begin{itemize}
\item \bibentry{Goodfellow2016}
\item \bibentry{Nielsen2015}. \url{http://neuralnetworksanddeeplearning.com/}
\end{itemize}

\section*{Papers}

\begin{itemize}
\item \bibentry{Domingos2012}. \url{https://homes.cs.washington.edu/~pedrod/papers/cacm12.pdf}
\end{itemize}

\section*{Videos}

\begin{itemize}
\item Grand Sanderson (3Blue1Brown). Deep Learning YouTube series (feedforward nets). \url{https://www.youtube.com/playlist?list=PLZHQObOWTQDNU6R1_67000Dx_ZCJB-3pi}

\item Andrew Ng. Machine Learning (Stanford course videos). \url{https://www.youtube.com/playlist?list=PLLssT5z_DsK-h9vYZkQkYNWcItqhlRJLN}
\end{itemize}

\section*{Websites}

\begin{itemize}
\item CS231 Convolutional Neural Networks for Visual Recognition (notes from a Stanford course, their Module 1 is similar to parts of our course). \url{https://cs231n.github.io/}

\item Chris Olah. colah's blog (great visualizations for neural nets). \url{http://colah.github.io/}

\item Distill (great visualizations for neural nets). \url{https://distill.pub/}

\item Sebastian Ruder. An overview of gradient descent optimization algorithms. \url{https://ruder.io/optimizing-gradient-descent/}
\end{itemize}

\bibliographystyle{plainnat}
\nobibliography{NNReferences}

\end{document}